---
title: "Penguins reproducibility demo"
date: today
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| include: false
targets::tar_load(c(
  clean_penguins,
  species_summary,
  island_summary,
  body_mass_plot,
  model_summary
))
```

## Purpose

This report demonstrates how pipeline outputs can be consumed in a reproducible analysis report.
All results shown here are generated by the `targets` pipeline defined in `_targets.R` and loaded
directly from the pipeline cache — this document does not perform any analysis itself.

## Data

The Palmer penguins dataset contains measurements for `r nrow(clean_penguins)` penguins
across three species (*Adelie*, *Chinstrap*, and *Gentoo*) on three islands
(Biscoe, Dream, and Torgersen) in the Palmer Archipelago, Antarctica.

## Summary results

### By species

```{r}
knitr::kable(
  species_summary,
  digits     = 1,
  col.names  = c("Species", "n", "Mean body mass (g)", "SD body mass (g)")
)
```

### By island

```{r}
knitr::kable(
  island_summary,
  digits     = 1,
  col.names  = c("Island", "n", "Mean body mass (g)", "SD body mass (g)")
)
```

## Figure

```{r}
#| fig-cap: "Body mass (g) by species and island. Missing values and records with unknown sex are excluded."
body_mass_plot
```

## Model

We fit a linear regression of body mass (g) on species, island, and sex.

```{r}
knitr::kable(
  model_summary,
  digits    = c(NA, 1, 1, 2, 4, 1, 1),
  col.names = c("Term", "Estimate", "SE", "Statistic", "p-value", "95% CI lower", "95% CI upper")
)
```

## Reproducibility note

This report is rendered through the `targets` pipeline. All analyses shown here are defined
in `_targets.R` and implemented as functions in `R/`. To reproduce:

```r
targets::tar_make()
```
